Arrows for Parallel Computations

### 2017-10-25 paper/content/motivation.tex
minor

%Our Arrows-based interface is a high-level one.
We provide an Arrows-based type class and implementations for the three above mentioned parallel Haskells.
Instead of 
introducing a new low-level parallel backend in order to implement our
Arrows-based interface, we define a shallow-embedded DSL for Arrows. This DSL
is defined as a common interface with varying implementations in
the existing parallel Haskells. Thus, we not only define a parallel programming interface in a
novel manner - we tame the zoo of parallel Haskells. We provide a
common \ptcomment{quantify, e.g. less than 10 \%}, very low-penalty programming interface that allows to switch
the parallel backends at will. Further backends based on HdpH or a Frege implementation (on the Java Virtual Machine) are viable, too.

@@

We show that it is possible to define algorithmic skeletons with Arrows (Sections \ref{sec:map-skeletons},~\ref{sec:topology-skeletons}) and finally demonstrate that Arrow Parallelism is a viable alternative to existing approaches and prove that only low overhead is introduced in Section \ref{sec:benchmarks}, i.e. less than x\% \mbcomment{fix this after benchmarks are finally done}.

>>>>

%Our Arrows-based interface is a high-level one.
We provide an Arrows-based type class and implementations for the three above mentioned parallel Haskells.
Instead of 
introducing a new low-level parallel backend in order to implement our
Arrows-based interface, we define a shallow-embedded DSL for Arrows. This DSL
is defined as a common interface with varying implementations in
the existing parallel Haskells. Thus, we not only define a parallel programming interface in a
novel manner - we tame the zoo of parallel Haskells. We provide a
common \ptcomment{quantify, e.g. less than 10 \%} \mbcomment{we do this in the contributions section of the Introduction, enough?}, very low-penalty programming interface that allows to switch
the parallel backends at will. Further backends based on HdpH or a Frege implementation (on the Java Virtual Machine) are viable, too.

@@

We show that it is possible to define algorithmic skeletons with Arrows (Sections \ref{sec:map-skeletons},~\ref{sec:topology-skeletons}) and finally demonstrate that Arrow Parallelism is a viable alternative to existing approaches and prove that only low overhead is introduced in Section \ref{sec:benchmarks}, i.e. less than $1.7\%$ in cases outside of the error bar of the measurement. \mbcomment{fix this after benchmarks are finally done}.
